\chapter*{INTRODUCTION}							% Заголовок
\addcontentsline{toc}{chapter}{INTRODUCTION}	% Добавляем его в оглавление

\newcommand{\actuality}{Relevance of the problem.}
\newcommand{\aim}{The objective}
\newcommand{\tasks}{Task}
\newcommand{\defpositions}{\textbf{Основные положения, выносимые на~защиту:}}
\newcommand{\novelty}{Scientific novelty:}
\newcommand{\influence}{Scientific and practical significance}
\newcommand{\reliability}{\textbf{Степень достоверности}}
\newcommand{\probation}{\textbf{Апробация работы.}}
\newcommand{\contribution}{Personal contribution.}
\newcommand{\publications}{Publications.}

\input{../common/characteristic} % Характеристика работы по структуре во введении и в автореферате не отличается (ГОСТ Р 7.0.11, пункты 5.3.1 и 9.2.1), потому её загружаем из одного и того же внешнего файла, предварительно задав форму выделения некоторым параметрам
%
%%% регистрируем счётчики в системе totcounter
\regtotcounter{totalcount@figure}
\regtotcounter{totalcount@table}       % Если поставить в преамбуле то ошибка в числе таблиц
\regtotcounter{TotPages}               % Если поставить в преамбуле то ошибка в числе страниц

Volume and structure. Thesis consists of introduction, five sections, summary and two appendices. The full volume of the thesis is \formbytotal{TotPages}{pages}{}{}{} 
including~\formbytotal{totalcount@figure}{figures}{}{}{}
and~\formbytotal{totalcount@table}{tables}{}{}{}.
Bibliography consists of \formbytotal{citenum}{cites}{}{}{}.

In the first section, we consider the problem of text classification and make an overview of the basic concepts, models and criteria which exist to solve the text classification problem.

In the second section, we present the process how to transform raw texts into features vectors. Also, we describe in details theoretical basis of deep neural networks which we use for our experiments, pay attention to their possible benefits and drawbacks for solving particular problems.

The third section examines the software used for experiments, as well as a code with explanations and diagrams that reproduce the process text processing, models selection and evaluation. 

The fourth section contains the results and explanations of experiments. We compare models with different parameters and architecture. Also, we propose future development options.
