\chapter*{INTRODUCTION}							% Заголовок
\addcontentsline{toc}{chapter}{INTRODUCTION}	% Добавляем его в оглавление

\newcommand{\actuality}{\textbf{Relevance of the problem:}}
\newcommand{\aim}{\textbf{Objective}}
\newcommand{\tasks}{Task}
\newcommand{\defpositions}{\textbf{Основные положения, выносимые на~защиту:}}
\newcommand{\novelty}{\textbf{Scientific novelty:}}
\newcommand{\influence}{\textbf{Scientific and practical significance}}
\newcommand{\reliability}{\textbf{Степень достоверности}}
\newcommand{\probation}{\textbf{Апробация работы.}}
\newcommand{\contribution}{\textbf{Personal contribution.}}
\newcommand{\publications}{\textbf{Publications.}}

\input{../common/characteristic} % Характеристика работы по структуре во введении и в автореферате не отличается (ГОСТ Р 7.0.11, пункты 5.3.1 и 9.2.1), потому её загружаем из одного и того же внешнего файла, предварительно задав форму выделения некоторым параметрам
%
%%% регистрируем счётчики в системе totcounter
\regtotcounter{totalcount@figure}
\regtotcounter{totalcount@table}       % Если поставить в преамбуле то ошибка в числе таблиц
\regtotcounter{TotPages}               % Если поставить в преамбуле то ошибка в числе страниц

\textbf{Volume and structure.} Thesis consists introduction, five sections, summary and two appendix.
Full volume of thesis is \formbytotal{TotPages}{pages}{}{}{} 
with~\formbytotal{totalcount@figure}{figures}{}{}{}
and~\formbytotal{totalcount@table}{tables}{}{}{}.
Bibliography consists \formbytotal{citenum}{cites}{}{}{}.

In the first section I consider the problem of text classification and make an overview of the basic concepts, models and criteria which exists to solve the text classification problem.

In the second section, I present the process how to transform raw texts into features vectors. Also, I describe in details theoretical basis of deep neural networks which I use for my experiments, pay attention on their possible benefits and drawbacks for solving particular problems.

The third section examines the software used for experiments, as well as a code with explanations and diagrams that reproduce the process text processing, models selection and evaluation. 

The fourth section contains the results and explanations of experiments. I compare models with different parameters and architecture. Also, I propose future development options.
